Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-12 idp/documents/documentation/paper.tex
Updated description based curves diagram, other fixes.

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{content/output/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				Kurve's user interface constructed from Components. Components may contain a number of subcomponents, render themselves into a GTK\# context, and handle mouse and keyboards events. 

>>>>

			\begin{figure}[htb]
				\centering
				\includegraphics[width=115mm]{content/output/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				Kurve's user interface is constructed from \verb|Component|s. \verb|Component|s may contain a number of subcomponents, render themselves into a GTK\# context, and handle mouse and keyboards events. 
